Methods for Large Scale Learning to Rank

### 2014-11-20 report/Chapters/Results.tex
mooiere uitlijning figuren

\begin{figure}
\centering
\includegraphics[trim=0cm 5cm 0cm 5cm, scale=0.8]{gfx/time_single_logx.pdf}
\caption{Processing time of a single ListNet training iteration on a logarithmic data size axis}
\label{fig:listnet_train_time_log}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[trim=0cm 5cm 0cm 5cm, scale=0.7]{gfx/speedup_faceted.pdf}
\caption{Processing time of a single ListNet training iteration as a function of the number of data nodes in a cluster}
\label{fig:speedup_train_time}
\end{figure}

\begin{figure}
\centering
\includegraphics[trim=0cm 5cm 0cm 5cm, scale=0.8]{gfx/processing_speed_single_logx.pdf}
\caption{Processing speed of a a single ListNet training iteration on various data sets}
\label{fig:listnet_processing_speed}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[trim=3cm 5cm 0cm 5cm, scale=0.8]{gfx/time_single_logx.pdf}
\caption{Processing time of a single ListNet training iteration on a logarithmic data size axis}
\label{fig:listnet_train_time_log}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[trim=5cm 5cm 0cm 5cm, scale=0.7]{gfx/speedup_faceted.pdf}
\caption{Processing time of a single ListNet training iteration as a function of the number of data nodes in a cluster}
\label{fig:speedup_train_time}
\end{figure}

\begin{figure}
\centering
\includegraphics[trim=0cm 5cm 0cm 5cm, scale=0.8]{gfx/processing_speed_single_logx.pdf}
\caption{Processing speed of a single ListNet training iteration on various data sets}
\label{fig:listnet_processing_speed}
\end{figure}
